---
title: 'How to start with `checkdown`'
author: "George Moroz"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
 %\VignetteIndexEntry{How to start with checkdown}
 %\VignetteEncoding{UTF-8}
 %\VignetteEngine{knitr::rmarkdown}
editor_options: 
 chunk_output_type: console
---

## Installation

Get the stable version from CRAN:

```{r, eval=FALSE}
install.packages("checkdown")
```

… or get the development version from GitHub:

```{r, eval=FALSE}
install.packages("remotes")
remotes::install_github("agricolamz/checkdown")
```

## 1. Demo

The main goal of this package to create checking fields and boxes in `rmarkdown`. It could be used in class, when teacher share materials and tasks (as an `.html` page or an `.html` slides), so student can solve some problems and check themselves. It is really important since some students are too shy to ask a question, so you can create tasks that will check on the fly the understanding of the class material and give some hints to those students that get stuck. In contrast to the [`learnr`](https://rstudio.github.io/learnr/index.html) package the `checkdown` package works without `shiny` and could be stored as a simple `.html` page (e. g. on Github Pages). In contrast to the [`exams`](https://www.r-exams.org/) output the `checkdown` package creates interactive autochecking tasks. The interactive version of the [`exams`](https://www.r-exams.org/) output is bind to Blackboard Learn, that is really nice, but looks like an overkill for the simple task that `checkdown` solves.

Load the library:

```{r}
library(checkdown)
```

### 1.1 Ask question with the `check_question()` function

Imagine that we want to create a checkbox with the answer 4. All you need is to create a following chunk in your `rmarkdown` document:

```{r}
check_question(answer = 4)
```

It is possible to change wrong and right answer's messages using `wrong` and `right` arguments of the `check_question()` function. Let's create some more questions.

Solve 3+3:

```{r}
check_question(answer = 6, right = "correct", wrong = "not correct")
```

Type *la-la*:

```{r}
check_question(answer = "la-la")
```

It is possible to use `placeholder` argument in order to show what kind of answer you expect:

```{r}
check_question(answer = "la-la", placeholder = "ta-ta-ta")
```

Number of answers is not limited:

```{r}
check_question(answer = 1:5)
```

It is also possible to create a list of answers for students to choose:

```{r}
check_question("banana", options = c("apple", "banana", "bread"), type = "select")

check_question("banana", options = c("apple", "banana", "bread"), type = "radio")
check_question(c("banana", "apple"), options = c("apple", "banana", "bread"), type = "checkbox")
```

If the list of possible answers is small, it is possible to align them in one line using `alignment` argument:

```{r}
check_question("banana", options = c("apple", "banana", "bread"), type = "radio", alignment = "horizontal")
```

You can shuffle answers using the `random_answer_order` argument:

```{r}
check_question("banana", options = c("apple", "banana", "bread"), type = "radio", random_answer_order = TRUE)
```

If you don't want to give the possibility of automatically check your question, just put `NULL` in the `answer` argument:

```{r}
check_question(NULL, options = c("apple", "banana", "bread"), type = "radio")
```

### 1.2 Give some hints with the `check_hint()` function

Sometimes you know in advance what kind of mistakes will your students do. Some students are shy and don't like asking questions, so hints could partially solve this problem. Again all you need is to create a following chunk with the chunck atribute `results='asis'` in your `rmarkdown` document:

```{r}
check_hint("You can use the rmarkdown package")
```

Of course it is possible to change the message of the part that should be clicked, just use the `hint_title` argument:

```{r}
check_hint("You can use the rmarkdown package inside checkdown",
           hint_title = "CLICK HERE")
```

By default you need to click on the hint in order to make it appear, but this behaviour can be changed with the `type` argument:

```{r}
check_hint("You can use the rmarkdown package inside checkdown",
           hint_title = "Put mouse over here",
           type = "onmouseover")

check_hint("You can use the rmarkdown package inside checkdown",
           hint_title = "Double click here",
           type = "ondblclick")
```

It is possible to use Markdown inside messages:

```{r}
check_hint("- You can use `markdown` **inside** the [`chcekdown` package](https://agricolamz.github.io/checkdown/)",
           hint_title = "Click he`R`e")

check_question(answer = 4, 
               wrong = "a**R**e you su**R**e?", 
               right = "### `R`ight")
```

There is also a function for multiple hints:

```{r}
check_hints(hint_text = c("look into the hint 2", "look into the hint 1"),
            hint_title = c("hint 1", "hint 2"), 
            list_title = "list of hints")
```

## 2. Inserting images

Sometimes it is nice to use images as a question. It also could be useful to insert images in hints. In order to do it you need to use `insert_images()` function, and enumerate the correct answer.

```{r, eval=FALSE}
check_question(answer = 3, 
               type = "radio",
               options = insert_images(c("windows.png", 
                                         "mac.png",
                                         "linux.png"), 
                                       image_width = 30))
```

Arguments `image_width` and `image_height` also except vector of values in case you need different size for different pictures. It is also possible to create a picture during the session, save it and use in `checkdown` functions.

```{r, eval=FALSE}
tmp <- tempfile(fileext = ".png")
library(ggplot2)
ggplot(data = mtcars, aes(mpg, disp)) + geom_point()
ggsave(filename = tmp)
```

Let's use obtained picture in the hint (notice, how I used percantage in the `image_width` argument):

```{r, eval=FALSE}
check_hint(paste("Here is our plot: <br>", 
                 insert_images(tmp, image_width = "40%")))
```

It looks like it is better to change font size, if you want to change the size of the picture. 

## 3. Some important notes

- It is possible to avoid code in the output `.html`. Just use the chunk argument `echo=FALSE`.
- For now the package `checkdown` works only with html output and will not print anything for other outputs.
- Be careful with number precision: rounding could be different on different computers so if you ask your student to calculate `log(3/4)` it is possible that they will see only 6 or 7 numbers after the comma. So it make sense explicitly specify precision using `round()` function.

```{r}
log(3/4)
check_question(answer = round(log(3/4), 6))
```
